Fail Faster

### 2025-03-23 paper/paper.tex
type

This makes type-derivation a particularly elegant target of \name. Since the process of type derivation is completely automatic,
the end user does not need to understand the staging syntax---but more importantly, applying \name to type-derivation
means it is more likely for even naive strategies to find a bug. \tr{TODO}

@@

The variation in speedups raises a natural question: what 
determines how much a generator benefits from staging, \rand optimizations, or both?
One likely explanation is that the two techniques address different performance bottlenecks:
generators that sample more often benefit more from improved random sampling, while those that rely
heavily on generator library combinators gain more from staging.
To test this idea, we need measurable proxies that approximate a generator's reliance on its generator and randomness libraries.
For the former, we use the number of calls to \texttt{bind}---the central monadic generator function, extensively used both directly and within other combinators.
For the latter, we count the number of times a generator invokes the SplitMix sampling routine \texttt{next\_int64}.

@@

\subsubsection{Do staged type-derived generators reduce timeouts?}
In addition to \camlname's overall bug-finding speed, we evaluate 
the performance of its type-derived generators---specifically, 
whether they can transform previously intractable tasks into 
tractable ones. Out of 78 tasks that initially timed out, 
50 (64\%) completed successfully after our interventions. 
This suggests that staged type-derived generators can provide 
significant performance improvements for free---that is, without
 any additional effort from the user.
\section{Beyond Strict Functional Languages}
\label{section:other-langs}

>>>>

This makes type-derivation a particularly elegant target of \name. Since the process of type derivation is completely automatic,
the end user does not need to understand the staging syntax---but more importantly, \name
makes it it more likely that even naïve strategies will find a bug. \tr{TODO}

@@

The variation in speedups raises a natural question: what 
determines how much a generator benefits from staging, \rand optimizations, or both?
One likely explanation is that the two techniques address different performance bottlenecks:
generators that sample more often benefit more from improved random sampling, while those that rely
heavily on generator library combinators gain more from staging.
To test this idea, we use measurable proxies that approximate a generator's reliance on its randomness and generator libraries.
For the former, we use the number of calls to \texttt{bind}---the central monadic generator function, extensively used both directly and within other combinators.
For the latter, we count the number of times a generator invokes the SplitMix sampling routine \texttt{next\_int64}.

@@

\subsubsection{Do improved type-derived generators reduce timeouts?}
In addition to \camlname's overall bug-finding speed, we evaluate 
the performance of its type-derived generators---specifically, 
whether they can transform previously intractable tasks into 
tractable ones. Out of 78 tasks that initially timed out, 
50 (64\%) completed successfully after our interventions. 
This suggests that staged type-derived generators can provide 
significant performance improvements for free---that is, without
 any additional effort from the user.
\section{Beyond Strict Functional Languages}
\label{section:other-langs}
